---
title: "414HW2"
author: "Ningyuan Wang"
date: "9/18/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Desktop/STATS414")
```

### 1.

```{r, results="hide" }
# generate observations
library(MASS)
mu <- c(3,4)
sigma <- matrix(c(1.0,0.8,0.8,1.0),nrow=2)
set.seed(123)
datam <- data.frame(mvrnorm(100,mu,sigma))
colnames(datam) <- c("x","y")
```

a. The scatter plot is in part b. To save the space, we only show the code here. 
```{r}
plot(datam$x, datam$y, xlim = c(0,7), ylim = c(0,7))
```


b. The values for alpha_hat is 1.6969772, beta_hat is 0.7547914, sigma_hat is 0.5701, and r_squared is 0.6063.
```{r}
lm = lm(y~x, data = datam)
lm$coefficients
summary(lm)$sigma
summary(lm)$r.squared
plot(datam$x, datam$y, xlim = c(0,7), ylim = c(0,7))+ abline(lm)
```


c. 
The value of F-statistic is 150.91, and p-value is < 2.2e-16. Because p-value < alpha(=0.05), reject H_0. 
```{r}
# reduced model
lm0 = lm(y~1, datam)
# compare two models
anova(lm0, lm)
```

d.
The value of F-statistic is 5.5854, and p-value is 0.02008. Because p-value < alpha(=0.05), reject H_0. 
```{r}
lm1 = lm(y~offset(0.9*x), datam)
anova(lm1, lm)
```


### 2.
```{r, result = "hide"}
m0 <- lm(y ~ x -1 , data=datam)
summary(m0)
```

a.
```{r}
plot(datam$x, datam$y, xlim = c(0,7), ylim = c(0,7))+ abline(m0, lty=2)
```

b. 
No. The sum of residuals for the model without an intercept is 13.79104.
```{r}
sum(residuals(m0))
```

c. Hand-writtten part was attached below.
```{r}
sum(datam$x * residuals(m0))
sum(fitted.values(m0) * residuals(m0))
# cor(datam) # correlation coeeficeint r
# anova(lm) # anova table for the model
```

