---
title: "414HW3"
author: "Ningyuan Wang"
date: "9/25/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1.
```{r,results="hide"}
library(MASS)
mu <- c(3,4)
sigma <- matrix(c(1.0,0.8,0.8,1.0),nrow=2)
set.seed(123)
datam <- data.frame(mvrnorm(100,mu,sigma))
colnames(datam) <- c("x","y")
```
a.
In the following plot, the solid line represents the linear model with y as the response and x as the predictor. The dashed line represents the linear model reversing the roles of x and y. 
```{r}
lm = lm(y~x, data = datam)
lm_rev = lm(x~y, data = datam)
# summary(lm_rev)
newy = seq(-1, 8, length = 50)
newx = coef(lm_rev)[1] + coef(lm_rev)[2]*newy
plot(datam$x, datam$y, xlim = c(0,7), ylim = c(0,7))+ abline(lm) 
lines(newx, newy, lty = 2)
```

b.
The R_squared, T-stats associated with the predicotors and their respective p-values, F-stats and p-values from the two models are the same. 
```{r}
# r_squared
summary(lm)$r.squared
summary(lm_rev)$r.squared
# t-stats
summary(lm)$coefficients
summary(lm_rev)$coefficients

# f-stats
summary(lm)$fstatistic
summary(lm_rev)$fstatistic
# summary(lm)
# summary(lm_rev)
```

c.
Please check the hand-written part below.

### 2.
a.
```{r}
dat = read.csv("college.csv")
pairs(dat[, c("gradrat", "csat", "stufac", "rmbrd", "act")])
lm_dat = lm(gradrat ~ csat + private + stufac  + rmbrd + act, data = dat)
# summary(lm_dat)
```
b.
F-stat is 1.1251 and p-value is 0.342. Since p-value >0.05, do not reject H0.
```{r}
lm_t1 = lm(gradrat ~ csat + act, data = dat)
anova(lm_t1, lm_dat)
```

c.
F-stat is 0.6348 and p-value is 0.4272 Since p-value >0.05, do not reject H0.
```{r}
lm_t2 = lm(gradrat ~ offset(0.05*csat) + private + stufac  + rmbrd + act, data = dat)
anova(lm_t2, lm_dat)
```

d.
F-stat is 44.565 and p-value is close to 0. Since p-value <0.05, reject H0.
```{r}
lm_t3 = lm(gradrat ~ csat + private + stufac, data = dat)
anova(lm_t3, lm_dat)
```

e.
F-stat is 7.8216 and p-value is 0.006. Since p-value <0.05, reject H0.
```{r}
lm_t4 = lm(gradrat ~ csat + private + stufac  + I(rmbrd + act), data = dat)
anova(lm_t4, lm_dat)
```

### 3.
beta0_hat is 1, beta1_hat is -0.5, beta2_hat is 0.5. The estimates for beta0_hat and beta1_hat remain unchanged if beta2 is 0. 
```{r}
dat3 = matrix(c(1,0,-1,1,0,2), ncol = 2)
dat3 = as.data.frame(dat3)
colnames(dat3) = c("x", "y")

lm3 = lm(y~x + I(3*x^2 -2),  data = dat3)
lm3$coefficients
lm4 = lm(y~x, data = dat3)
lm4$coefficients

```

### 4. Please see the hand-written part below. 