---
title: "Quiz2"
author: "Ningyuan Wang"
date: "10/20/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nlme)
data(cars)
```

### 1.
a. 
The residuals does not sum to zero, but the weighted residuals sum to zero. 
b. 
Based on the result of F-test, since p<0.05, reject H0 (i.e. weighted reduced model with only the intercept). According to the ANOVA table, SST is 97.019, SSR is 69.028, and SSE is 27.990, so SSE + SSR = SST. The codes for SST and SSR confirm the above results. 
```{r }
# a.
m1 = gls(dist ~ speed, data = cars, weight = varConstPower(1, form=~speed))
summary(m1)
sum(resid(m1)) # 20.46435, ???is different if 0.76^2*48
myweights = (3.1604+cars$speed^1.0224)^(-2)
sum(myweights*resid(m1)) # 4.878433e-06
# b.
m2 = lm(dist ~ speed, data = cars, weight = myweights)
m0 = lm(dist ~ 1, data = cars, weight = myweights)
anova(m0, m2)
# SST, SSR, SSE
y_bar = coef(m0) # 28.60139
sst = sum(myweights*((cars$dist - y_bar)^2)) # 97.01857
ssr = sum(myweights*((fitted(m1) - y_bar)^2)) # 69.02904
```

### 2.
a. 
The model result shows below.
b. 
They results of the parameter estimates and standard errors calculated based on the Fisher scoring algorithm is same to the model results.
```{r, include = FALSE}
acc <- c(188,107,63,23,241,92,61,19,200,118,22,19,21,13,11,1,31,11,5,0,26,17,2,6)
trav <- c(204433874,177250749,41949294,29883757,128647023,59822202,17642351,6838521,31765363,59730974,1289058,3775431,23163210,21162524,9473358,3474259,15040022,5529527,2400560,459525,3207263,4951688,224036,340844)
truck <- gl(2,12)
road <- gl(3,4,length=24)
time <- gl(2,2,length=24)
area <- gl(2,1,length=24)
logtrav <- log(trav)
dataf <- data.frame(truck=truck,road=road,time=time,area=area,acc=acc,trav=trav,logtrav=logtrav)
```

```{r}
m3 <- glm(acc ~ truck + road + time + area + road*time + road*area,family=poisson, offset=logtrav, data=dataf)
summary(m3)
```

b.
```{r}
obsrate = acc/trav
acc1 = ifelse(acc==0, 0.5,acc)
obsrate1  = acc1/trav
mu = obsrate1
eta = log(mu)
z = eta
w = acc1

for (i in 1:5){
  mod = lm(z ~ truck + road + time + area + road*time + road*area,
           weights = w)
  eta = fitted(mod)
  mu = exp(eta)
  z = eta + (obsrate - mu)/mu
  w = trav*mu
}
coef(mod)
varbeta = summary(mod)$cov.unscaled
sqrt(diag(varbeta))
  
```


